Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
teaser

 \teaser{
   \begin{subfigure}[b]{0.3\textwidth}
	\centering
    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{A textured mesh printed with different types of 3D printers.
        	(a)original model.(b)printed with our printer.(c)makerbot.
        	(d)objet}\label{teaser}
 }

>>>>

 \teaser{
   \begin{subfigure}[b]{0.2\textwidth}
	\centering
    	\includegraphics[width=\textwidth]{figure/globe.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/map.png}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/chess.png}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/caustics.png}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{Various effects printed with a 3D printer.
        	(a)(b)textured models,(c)a model with a subsurface-scattering resembling a marble chess-board.
        	(d)a caustics image projected by an object under proper lighting}\label{teaser}
 }
